---
title: "Report"
author: "Christina De Cesaris"
date: "3/13/2021"
output: html_document
---


# Introduciton and Background


## Methodology


# Exploratory Analysis 

```{r Libraries, echo=FALSE, warning=FALSE}

# plotting 
library(redres)
library(ggplot2)
library(plotly)


# analysis
library(MASS)
library(tidyverse)
library(lmerTest)
library(scales)


# formatting
library(grid)
library(gridExtra)
library(stargazer)

# data
library(AER)
library(DT)
data(Guns)
```

```{r Summary Dataframes, warning=FALSE, include=FALSE}


av_st = Guns %>%
  group_by(state) %>% # average all state
  summarise_all(mean) %>%
  mutate_if(is.numeric,funs(round(.,2)))
av_st
#av_st


av_st_r = Guns %>%
  group_by(state) %>% # average all state
  summarise(mean(violent),median(violent), sd(violent), max(violent), min(violent))%>%
  mutate_if(is.numeric,funs(round(.,2)))
av_st_r


av_yr_r = Guns %>%
  group_by(year) %>% # average all state
  summarise(mean(violent),median(violent), sd(violent), max(violent), min(violent))%>%
  mutate_if(is.numeric,funs(round(.,2)))
av_yr_r

av_styr = Guns %>%   # average each year each state
  group_by(year,state) %>%
  summarise_all(mean)%>%
  mutate_if(is.numeric,funs(round(.,2)))
av_styr

av_yr = Guns %>% # average all states each years
  group_by(year)%>%
  summarise_all(mean)%>%
  mutate_if(is.numeric,funs(round(.,2)))

#delete null cols
av_yr=dplyr::select(av_yr,-c(6,7,12,13))
av_st=dplyr::select(av_st,-c(2,7,8,13))
```


```{r Yearly Trends All States Plots}



v=Guns %>%
  ggplot( 
    aes(x=year,
        y=violent,
        group=state,
        color=state)) +
    geom_line() +
    labs(
      title="Yearly Trends in Violent Crime by State",
      x="School ID",
      y = "Violent Crime Rate per 100K Poeple") +
    theme(
      text = element_text(
        size=8,
        face = 'bold'),
        axis.text.x = element_text(angle=75,hjust=1),
        axis.ticks.x = element_line(size=0.5)) +
     scale_x_discrete(
       guide = guide_axis(n.dodge =1),
                     expand=c(0, 0)) +
    scale_fill_discrete(name = "State")


#ggplotly(v)

r = Guns %>%
  
  ggplot( 
    aes(x=year,
        y=robbery,
        group=state,
        color=state)) +
    geom_line() +
    labs(
      title="Yearly Trends in Robbery Crime by State",
      x="School ID",
      y = "Robbery Crime Rate per 100K People") +
    theme(
      text = element_text(
        size=8,
        face = 'bold'),
        axis.text.x = element_text(angle=75,hjust=1),
        axis.ticks.x = element_line(size=0.5)) +
     scale_x_discrete(
       guide = guide_axis(n.dodge =1),
                     expand=c(0, 0)) +
     scale_fill_discrete(name = "State")


#ggplotly(r)


m = Guns %>%
  
  ggplot(
    aes(x=year,
        y=(violent),
        group=year,
        col=year)) +
    geom_boxplot()+
  labs(
      title="USA Violent Crime by Year",
      x="Year",
      y = "Violent Crime Rate per 100K People") +
    theme(
      text = element_text(
        size=8,
        face = 'bold'),
        axis.text.x = element_text(angle=75,hjust=1),
        axis.ticks.x = element_line(size=0.5)) +
     scale_x_discrete(
       guide = guide_axis(n.dodge =1),
                     expand=c(0, 0)) +
    scale_fill_discrete(name = "year")


#ggplotly(m) # DC is a gross outlier, consider removal 


```


```{r Interactive Datatables, include=FALSE}

names_yr=c("Year","Violent Crime Rate","Murder Rate","Robbery Rate","Prisoners","Percent Male","Population", "Income","Density")

dt_av_yr=datatable(av_yr,
          class = 'cell-border stripe',
          caption = htmltools::tags$caption(style = 'caption-side: bottom; text-align: center;','Table 1: ',
    htmltools::em(
      'Overall Averages By State')),
    colnames = c(
      names_yr))



names_st=c("State","Violent Crime Rate","Murder Rate","Robbery Rate","Prisoners","Percent Male","Population", "Income","Density")
dt_av_st=datatable(av_st,
          class = 'cell-border stripe',
          caption = htmltools::tags$caption(style = 'caption-side: bottom; text-align: center;','Table 1: ',
    htmltools::em(
      'Overall Averages By State')),
    colnames = c(
      names_st))



#RESPONSE


names_av_st_r=c("State","Mean Violence Rate", "Median Violence Rate", "Standard Deviation Violence Rate","Max Violence Rate","Min Violence Rate" )

dt_av_st_r=datatable(av_st_r,
          class = 'cell-border stripe',
          caption = htmltools::tags$caption(style = 'caption-side: bottom; text-align: center;','Table 1: ',
    htmltools::em(
      'Overall Averages By State')),
    colnames = c(
      names_av_st_r))



names_av_yr_r=c("Year","Mean Violence Rate", "Median Violence Rate", "Standard Deviation Violence Rate","Max Violence Rate","Min Violence Rate" )

dt_av_yr_r=datatable(av_yr_r,
          class = 'cell-border stripe',
          caption = htmltools::tags$caption(style = 'caption-side: bottom; text-align: center;','Table 1: ',
    htmltools::em(
      'Overall Averages By State')),
    colnames = c(
      names_av_yr_r))


```

```{r Average Crime USA, include=FALSE}



crime_fig <- plot_ly(av_yr, x= ~year) %>%
  add_lines(
    y= ~(violent),
    name = "Violent Crime",
    type = 'scatter',
    mode = 'lines+markers') %>%
  
  add_lines(
    y= ~(robbery),
    name = "Robberies",
    visible = T) %>%
  
  add_lines(
    y= ~(murder),
    name = "Murder",
    visible = T) %>%
  
    layout(
      title = "Average Crime Rates in USA",  
      xaxis = list(title = "Year",
                   tickangle = 75),
      yaxis = list(title = "Average per 100k People",
                   margin = margin)) 





```







# Inferential Analysis



# Sensitivity Analysis




# Conclusions

# References

(Brookhart et al. 2014)

Brookhart, M. A., Wyss, R., Layton, J. B., & Stürmer, T. (2013). Propensity score methods for confounding control in nonexperimental research. Circulation. Cardiovascular quality and outcomes, 6(5), 604–611. https://doi.org/10.1161/CIRCOUTCOMES.113.000359


(Kleiber & Achim, 2008)

Kleiber, C. & Zeileis, A. (2008). Applied Econometrics with R. Springer-Verlag.


(Miller et. al, 2002)

Miller, M., Azrael, D., & Hemenway, D. (2002). Rates of household firearm ownership and homicide across US regions and states, 1988-1997. American journal of public health, 92(12), 1988–1993. https://doi.org/10.2105/ajph.92.12.1988




(Zimring, 2004)

Zimring, F. (2004). Firearms, Violence, and the Potential Impact of Firearms Control. Journal of Law, Medicine & Ethics, 32(1), 34-37. doi:10.1111/j.1748-720X.2004.tb00446.x



# Code Appendix

```{r ref.label=knitr::all_labels(), echo = T, eval = F}
```
